A partisan affair: Mapping patronage in municipal bureaucracies of Brazil

### 2021-03-29 paper/draft.tex
add data pipeline

>>>>

\subsection{Joining Public Sector Employment to Partisanship Data}
One of the main contributions of this paper is performing a join of public sector employment data to partisanship data, to allow us to identify and follow partisan affiliates in their entire career. The key challenge in joining is the low coverage of keys that allow for a unique match across these databases. The problem is as follows. Only a subset of party members have the unique national id, \emph{CPF},associated with their registration, which is uniquely identified by the national electoral title (\emph{t'{i}tulo eleitoral}).

To maximize coverage, the party membership data is first joined to the candidacy data generated by the \emph{TSE} for every electoral cycle using the electoral title as the key. This allows us to recover over 300 thousand national id's. Additionally, we use the complete names of both the party members and the \emph{RAIS} employees to perform an exact name match for every municipality in the dataset for active employees and party members, by year. To prevent many to many merges, complete names are deduplicated by municipality, our smallest geographical unit. Deduplication leads only to minimal data loss: for the \emph{RAIS} data we exclude around 6 percent of the names database per year, while for the party membership data we exclude around 5 percent.

In total, we achieve the match of 18.5 million unique matches between the the \emph{RAIS} dataset and the party membership data. To give a sense of the scale of the data ETL (extraction, transformation and loading): in the year of 2015 there were in total 54 million employees in the \emph{RAIS} data, while in the party membership there were 9.2 million active membership ties. Partitioning the data into manageable chunks requires the development of both a semantic layer and data pipelines that are often beyond the scope of political science and enter the domain of data science and functional programming that fall under the domain of computer science.\footnote{For great resources on the topic, see the following \href{https://r4ds.had.co.nz/index.html}{\emph{R for Data Science}} resource.}
